---
title: "Cycling Accessibility Across Toronto Neighbourhoods"
author:
- name: Julianna Filice (400457494)
- name: Daniella Frost (400443436)
- name: Jeewoo Kang (400455227)
- name: Abigail Wilson (400460081)
- name: Joyce Wu (400452669)
subject: "ENVSOCTY 4GA3 - Applied Spatial Statistics"
date: "`r format(Sys.time(), '%d %B, %Y')`"

abstract: "This report is discussing our assessment of _____"

keywords: "Bikeshare, accessibility, socioeconomic inequalities, spatial analysis"


output:
  pdf_document:
    # The project-template-default.tex file was heavily  adapted from Steven V. Miller's template for academic manuscripts. See:
    # http://svmiller.com/blog/2016/02/svm-r-markdown-manuscript/
    # https://github.com/svmiller/svm-r-markdown-templates/blob/master/svm-latex-ms.tex
    template: exercise-template-default.tex
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())
```
---
<!--Use "#" for section headers-->

#Introduction

This is our introduction 


#Background

This is our background


#Study Area

This is our study area, why we chose this place, what the significance entails


#Data

This is our data, how we formatted, etc... 


#Methods

How did we perform the assessment, what did we decide to assess and why. Rationale for tests and maps


#Results 

What did we find


#Analysis 

This is the signficance of our results


#Conclusion 

Restate project objectives/purpose


#References

list in APA 7th: I don't know if we need a special thing to format the bibliography: verify on that






